Estimating SARS-CoV-2 transmission in England from randomly sampled prevalence surveys

### 2024-02-13 introduction.tex
proof read ATACCC
ch 3 proofing

\begin{itemize}
    \item Infectious disease epidemiology and biostatistics heavily developed in context of HIV/AIDS epidemic
    \item Use much methodology and concepts from this field
\end{itemize}

@@

\begin{itemize}
    \item Duration is important
    \item Mathematical details in \cref{E-inc-prev}
\end{itemize}

@@

>>>>

\begin{itemize}
    \item Infectious disease epidemiology and biostatistics heavily developed in context of HIV/AIDS epidemic
    \item Use much methodology and concepts from this field
    \item Surveillance in general (incidence)
\end{itemize}

\subsection{Surveillance}

\begin{itemize}
    \item Reproduction numbers
    \item Incidence: almost never observed directly
\end{itemize}

@@

\begin{itemize}
    \item Duration is important
    \item Mathematical details in \cref{E-inc-prev}
    \item Infection process well established, what needs adapting for here (recoveries, sampling)? See first-year report.
\end{itemize}

@@

Expand on this biomarker vs survival analysis comparison
\begin{itemize}
    \item Why do I apply each method?
    \item Biomarker: stronger assumptions but more information used.
    \item Literature review on estimates of length of PCR positivity (none in general pop)
\end{itemize}

\section{Notational conventions}

\begin{itemize}
    \item Lower-case variables are realisations of the respective upper-case random variables.
    \item Matrices and vectors are bold and have elements with the same unbolded letter, \eg $\vec{x} = [x_1, x_2, \dots]^T$
\end{itemize}

### 2024-02-13 transmission.tex
ch 3 proofing

% Here, I extend the system of ODEs to include compartments representing RT-PCR positive individuals.
% The proportion of RT-PCR positive individuals in each strata is then linked to the CIS using a Beta-Binomial likelihood, with the modelled proportion that are RT-PCR positive as the mean of the Beta distribution.
One approach would be to convolve the incidence based on the transmission model with the RT-PCR duration distribution.
Here, the daily incidence proportion for each stratum derived by solving the system of ODEs governing the transmission model, and then prevalence calculated using \cref{E-inc-prev:eq:EPt}.
However, this approach is computationally expensive, likely prohibitively so if performed within a MCMC loop.

>>>>

% Here, I extend the system of ODEs to include compartments representing RT-PCR positive individuals.
% The proportion of RT-PCR positive individuals in each strata is then linked to the CIS using a Beta-Binomial likelihood, with the modelled proportion that are RT-PCR positive as the mean of the Beta distribution.
One approach would be to convolve the incidence based on the transmission model with the RT-PCR duration distribution.
Here, the daily incidence proportion for each stratum derived by solving the system of ODEs governing the transmission model (see \cref{E-SEIR:sec:SIR}), and then prevalence calculated using \cref{E-inc-prev:eq:EPt}.
However, this approach is computationally expensive, likely prohibitively so if performed within a MCMC loop.
